Pigeons.jl: Distributed sampling from intractable distributions

### 2023-10-31 paper/header.tex
fix

\keywords{Distributed computation, Bayesian inference, parallelism invariance, 
multi-threading, Message Passing Interface, Markov chain Monte Carlo}

\hypersetup{
pdftitle = {My JuliaCon proceeding},
pdfsubject = {JuliaCon 2019 Proceedings},
pdfauthor = {1st author, 2nd author, 3rd author},
pdfkeywords = {Julia, Optimization, Game theory, Compiler},
}

>>>>

\keywords{distributed computation, Bayesian inference, parallelism invariance, multi-threading, Message Passing Interface, Markov chain Monte Carlo}

\hypersetup{
pdftitle = {Pigeons.jl: Distributed sampling from intractable distributions},
pdfsubject = {JuliaCon 2022 Proceedings},
pdfauthor = {Nikola Surjanovic, Miguel Biron-Lattes, Paul Tiede, Saifuddin Syed, Trevor Campbell, Alexandre Bouchard-Côté},
pdfkeywords = {distributed computation, Bayesian inference, parallelism invariance, multi-threading, Message Passing Interface, Markov chain Monte Carlo},
}
